Comparing Power Optimizations in the Reorder Buffer

### 2011-06-08 paper/proj.tex
Results table now in implementation tex, but correctly shows up in results section.

>>>>

\begin{table*}[!tb]
\centering
\caption{FP Heavy Instruction Profile Results(B1)}
\begin{tabular}{|c|c|c|c|c|c|} \hline
    & Circular  & Distrubuted & Dynamic & Dynamic (optimized) & OOP\\ \hline
Cycles&82,722	&50,541&    	84,211	&84,078&        	82,153\\ \hline
Bit Cycles&1,483,701,792&	1,399,581,372&	1,453,144,453	&1,470,555,825	&1,522,130,784\\ \hline
Trans. to High&1,967,483&	1,719,957	&1,942,948	&1,930,476	&3,235,293\\ \hline
Reg Comp&6,725,088&	6,631,913&	6,710,777&	6,718,043	&11,160,291\\ \hline
\end{tabular}
\end{table*}

\begin{table*}[!tb]
\centering
\caption{int Heavy Instruction Profile Results(B2)}
\begin{tabular}{|c|c|c|c|c|c|} \hline
    & Circular  & Distrubuted & Dynamic & Dynamic (optimized) & OOP\\ \hline
Cycles&25,781&	25,794&	26,079	&25,783	&25,780\\ \hline
Bit Cycles&462,408,016	&714,287,448	&310,408,263	&317,109,601	&477,651,840\\ \hline
Trans. to High&1,347,679&	1,134,479	&1,363,418&	1,369,396	&2,262,036\\ \hline
Reg Comp&3,220,687	&3,221,904	&3,219,866	&3,221,335&	5,155,838\\ \hline
\end{tabular}
\end{table*}

\begin{table*}[!tb]
\centering
\caption{Mix Instruction Profile Results(B3)}
\begin{tabular}{|c|c|c|c|c|c|} \hline
    & Circular  & Distrubuted & Dynamic & Dynamic (optimized) & OOP\\ \hline
Cycles&29,858	&29,914	&31,733	&30,509	&29,845\\ \hline

Bit Cycles&535,533,088&	828,378,488&	352,433,432	&342,715,483	&552,968,160\\ \hline

Trans. to High&4,591,862	&4,585,663	&4,588,186&	4,603,780&	6,758,124\\ \hline

Reg Comp&1,688,252&	1,436,544	&1,655,666	&1,657,563	&2,802,135\\ \hline
\end{tabular}
\end{table*}
